EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-04-30 draft.tex
Proposal for #5
Starting new section

The main advantage of container deployments over virtual machine
instances is that they add much less overhead to communication between
them, and they are much more economical to deploy. Scaling and
monitoring can be done much more easily through cloud orchestration
systems such as Kubernetes; these are the reasons why we chose it for
this work.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario
% Did you finally? - JJ

In this section, we propose a design of a reactive container-based application
for executing multi-population based optimization experiments.  For the design,
we followed the design patterns highlighted in the previous section, and again
we can go back to Figure \ref{fig:kafkEO} and use it as a guide for explaining
the main components and their interactions.

@@

% Maybe you should say here how everything wors: launch with
% Docker-compose, whatever. That's the issue that one of the reviewers
% say - JJ
\subsection{Worker Containers} 
\label{workers}

@@

\subsection{Experimental Workflow in EvoSwarm} 
\label{experiment_flow}

@@

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file
% Fi file? - JJ+
% fixed - Mario
to specify the type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

>>>>

The main advantage of container deployments over virtual machine
instances is that they add much less overhead to communication between
them, and they are much more economical to deploy. Scaling and
monitoring can be done much more easily through cloud orchestration
systems such as Kubernetes; these are the reasons why we chose it for
this work.
% I don't see this line of argument. You can do exactly the same with
% virtual machines instead of containers. Also, you can test a virtual
% infrastructure locally and then only when it's needed deploy it to
% the cloud. If you want to give good reasons for using containers
% instead of virtual machines, there are quite a lot non-economic ones
% - JJ
% OK, I will add an issue - Mario
% Did you finally? - JJ
% I did not, will add and assign it - M 
In this section, we propose a design of a reactive container-based application
for executing multi-population based optimization experiments.  For the design,
we followed the design patterns highlighted in the previous section, and again
we can go back to Figure \ref{fig:kafkEO} and use it as a guide for explaining
the main components and their interactions.

@@

% Maybe you should say here how everything wors: launch with
% Docker-compose, whatever. That's the issue that one of the reviewers
% say - JJ

% This issue is also commanted in the experimental section
% I will explain it and then we can see where it goes. - M

\subsection{Worker Containers} 
\label{workers}

@@

\section{Experimental Workflow in EvoSwarm} % We could upgrade this to a section and explain in detail 
% taking care of #5 - M
\label{experiment_flow}

Figure \ref{fig:experiment_flow} shows the general workflow to run experiments 
in Evo\-Swarm, and three roles users can play. The first step is to develop the 
search strategy algorithms that are going to be used by the multi-population algorithm.

Figure \ref{fig:experiment_flow} shows the general workflow to run experiments
in Evo\-Swarm, and three roles users can play. The first step is to develop the
search strategy algorithms that are going to be used by the multi-population
algorithm; algorithm developers do this. Then administrators are responsible for
the installation and configuration of the application. Once the application is
running, users can start one or several experiments, monitor the execution, and
analyze the results. Depending on the type of experiment executed, users could
have additional needs. As a use case, there are additional scripts for
processing the results of experiments to be used with the COCO framework. In the
next sections, we give more details about these roles and their workflow.

@@

\subsection{Developer}

\subsection{EvoSwarm Configuration}

\subsection{Experiment Execution}

\subsection{Using the COCO Framework}
% BBOB Cases

The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub; another option is to upload the container image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub; this
can be defined in DockerHub (or any other registry) too.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file
to specify the type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers, downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script
that takes as argument the
experiment id to generate a collection of files containing all the
data generated by the experiment in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper;  there is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.
